Gozde and Liora Replication Code

### 2015-04-10 Gozde-Liora-Replication-Code.Rmd
Adding images from paper to our code

# Table 1

```{r}
# Create vectors of coefficients, standard deviations, and variable names

@@

# Figure 1 (Conditonal Effects of Unemployment and Immigration)

```{r}
library(msm)
asy <- seq(from = -.98, to = 4.46, by = .01) # vector with possible values for asylumseekers
variable <- asy # to standardize the code
slopes <- model$coef$fixed[17] + model$coef$fixed[36] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for each variable 
var <- vcov(model) # Estimated variances
se <- rep(NA, length(asy))

@@

# Figure 2 (Conditonal Effects of Salience and Variance)

```{r}
# Graph 1
salience <- seq(from = -3.108026, to = 21.872906, by=.1) # vector with possible values for salience
variable <- salience
slopes <- model$coef$fixed[21] + model$coef$fixed[39] * variable # Estimated slopes based on estimated coefficients of salience (21) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for each variable 
var <- vcov(model)
se <- rep(NA, length(variable))

>>>>

# Table 1
![Table 1](figures/table1.png)
```{r}
# Create vectors of coefficients, standard deviations, and variable names

@@

# Figure 1 (Conditonal Effects of Unemployment and Immigration)
![Figure 1](figures/fig1.png)
```{r}
library(msm)
asy <- seq(from = -.98, to = 4.46, by = .01) # vector with possible values for asylumseekers
variable <- asy # to standardize the code
slopes <- model$coef$fixed[17] + model$coef$fixed[36] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for each variable 
var <- vcov(model) # Estimated variances
se <- rep(NA, length(asy))

@@

# Figure 2 (Conditonal Effects of Salience and Variance)
![Figure 2](figures/fig2.png)
```{r}
# Graph 1
salience <- seq(from = -3.108026, to = 21.872906, by=.1) # vector with possible values for salience
variable <- salience
slopes <- model$coef$fixed[21] + model$coef$fixed[39] * variable # Estimated slopes based on estimated coefficients of salience (21) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for each variable 
var <- vcov(model)
se <- rep(NA, length(variable))
